Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-16 ieee_paper.tex
using raster version of spyplots

\def\ww{.13\textwidth}
\begin{figure*}
  \begin{center}
    \subfigure[Supercompact.]{%
      \label{fig:supercompact}
      \includegraphics[width=\ww]{figures/supercompact_matrix-crop.pdf}}%
    \subfigure[Compact.]{%
      \label{fig:compact}
      \includegraphics[width=\ww]{figures/compact_matrix-crop.pdf}}%
    \subfigure[Random.]{%
      \label{fig:random}
      \includegraphics[width=\ww]{figures/random_matrix-crop.pdf}}%
    \subfigure[2D, no RCM.]{%
      \label{fig:rbf2dnorcm}
      \includegraphics[width=\ww]{figures/kd-tree-2d-norcm-crop.pdf}}%
    \subfigure[2D, RCM.]{%
      \label{fig:rbf2drcm}
      \includegraphics[width=\ww]{figures/kd-tree-2d-rcm-crop.pdf}} 
    \subfigure[3D, RCM.]{%
      \label{fig:rbf3dnorcm} 
      \includegraphics[width=\ww]{figures/kd-tree-3d-norcm-crop.pdf}}%
    \subfigure[3D, RCM.]{%
      \label{fig:rbf3drcm}
      \includegraphics[width=\ww]{figures/kd-tree-3d-rcm-crop.pdf}}%
  \end{center}

>>>>

\def\ww{.13\textwidth}
\begin{figure*}
  \begin{center}
    \subfigure[Supercompact.]{%
      \label{fig:supercompact}
      \includegraphics[width=\ww]{figures/supercompact_matrix-crop.png}}%
    \subfigure[Compact.]{%
      \label{fig:compact}
      \includegraphics[width=\ww]{figures/compact_matrix-crop.png}}%
    \subfigure[Random.]{%
      \label{fig:random}
      \includegraphics[width=\ww]{figures/random_matrix-crop.png}}%
    \subfigure[2D, no RCM.]{%
      \label{fig:rbf2dnorcm}
      \includegraphics[width=\ww]{figures/kd-tree-2d-norcm-crop.png}}%
    \subfigure[2D, RCM.]{%
      \label{fig:rbf2drcm}
      \includegraphics[width=\ww]{figures/kd-tree-2d-rcm-crop.png}} 
    \subfigure[3D, RCM.]{%
      \label{fig:rbf3dnorcm} 
      \includegraphics[width=\ww]{figures/kd-tree-3d-norcm-crop.png}}%
    \subfigure[3D, RCM.]{%
      \label{fig:rbf3drcm}
      \includegraphics[width=\ww]{figures/kd-tree-3d-rcm-crop.png}}%
  \end{center}
